 \addcontentsline{toc}{chapter}{Список литературы}
\begin{thebibliography}{3}
	\bibitem{crypto} Харин Ю.С., Берник В.И., Матвеев Г.В., Агиевич С.В. Математические и компьютерные основы криптологии. -- 2003. -- Минск.
	
	\bibitem{crypto_nn} Neural networks in cryptography [Электрон. ресурс]. -- 2015. -- 
	$\underline{http://cryptowiki.net/index.php?}$\\
	$\underline{title=Neural\_networks\_in\_cryptography}$.
	\bibitem{encr_nn} Pattanayak S., Ludwig S.A. Encryption based on Neural Cryptography. -- 2017.
	\bibitem{clark}Clark M., Blank D. A Neural-Network Based Cryptographic System. -- 1998
	
	\bibitem{kinzel} Kinzel F., Kanter I. Neural Cryptography. — 2002.
	\bibitem{lis} Li S. Analyses and New Designs of Digital Chaotic Ciphers. -- 2003. -- China.
		\bibitem{rao} Rao K., Krishna M., Babu D. Cryptanalysis of a Feistel Type Block Cipher by Feed
	Forward Neural Network Using Right Sigmoidal Signal. -- 2009.
	\bibitem{neuro_des} Mohammed M. Alani.Neuro-Cryptanalysis of DES and Triple-DES. -- 2012.
	\bibitem{practice} Харин Ю.С., Агиевич С.В. Компьютерный практикум по математическим методам защиты информации. -- 2001. -- Минск.
	
	\bibitem{bnb} Minjie K., Smaragdis P. Bitwise Neural Network. -- 2016.
	\bibitem{towards} Lin X., Cong Z., Wei P. Towards Accurate Binary Convolutional NeuralNetwork. -- 20017.
	\bibitem{implement} Implementing the XOR Gate using Backpropagation in Neural Networks [Электрон. ресурс]. — 2019. — $\underline{https://towardsdatascience.com/implementing-the-xor-gate-using-backpropagation-in-neural-networks-c1f255b4f20d}$.
	\bibitem{permutation} Sannai A., Takai Y., Cordonnier M. Universal approximations of permutation in-variant/equivariant functions by deep neural networks. -- 2019.
	
	
	\bibitem{knudsen} Knudsen L.R. Block Ciphers -- 1998.
\bibitem{godhavari} Godhavari T., Alamelu N.R., Soundararajan R. Cryptography Using Neural Network. -- 2005.

	\bibitem{kanter} Kanter K.W., Kanter E. Secure exchange of information by synchronization of neural
	networks. -- 2002.
	\bibitem{klimov} Klimov A.B., Mityagin A., Shamir A.: Analysis of Neural Cryptography. -- 2002.
	\bibitem{li} Li L., Lin L., Hwang M. A remote password authentication scheme for multiserver ar-
	chitecture using neural networks. -- 2001.
	\bibitem{dourlens} Dourlens, S. Neuro-Cryptography. -- 1995. -- France.

	\bibitem{lic} Li C., Li S., Zhang D., Chen G. Chosen-Plaintext Cryptanalysis of a Clipped-Neural-
	Network-Based Chaotic Cipher. -- 2005.

	\bibitem{alani} Alani M.M. Neurocryptanalysis of DES. -- 2012.
    
\end{thebibliography}

